%!TEX root = ../giuseppe-cv.tex
%----------------------------------------------------------------------------------
%            Projects
%----------------------------------------------------------------------------------
\section{Projects}
	\cventry{2017}{Twitch Chat Bot and Notification System}{Team of 2}
		{\newline Implemented an IRC chat bot to process and respond to Twitch chat messages. Implemented a websocket server
		to provide notifications to a web browser}
		{}{}
	\cventry{Spring 2014}{Operating Systems Implementation, UNC Chapel Hill}{Team of 3}
		{\newline Implemented three custom I/O schedulers in the Linux kernel and benchmarking performance using IOZone and Bonnie++}
		{}{}
	\cventry{Fall 2013}{Wireless Networks, UNC Chapel Hill}{Team of 2}
		{\newline Designed an experiment to observe and analyze the 802.11 channel capture effect}
		{}{}
	\cventry{Fall 2013}{Distributed Systems, UNC Chapel Hill}{Solo}
		{\newline Converted a standard non-distributed application to a distributed application. Multiple libraries to handle
		RPC were used including Java NIO, Java RMI, and custom libraries which explored other synchronous
		and asynchronous approaches}
		{}{}
	\cventry{Fall 2013}{Big Data, UNC Chapel Hill}{Team of 2}
		{\newline Developed a travel prediction model based on latent factors of travel. Factors learned using Batch
		Gradient Descent. Latent factors were the desirability of a location and a distance-time factor reflecting
		how far a person may travel in a given time}
		{}{}
	\cventry{Spring 2010}{Senior Project, USF}{Team of 4}
		{\newline Designed an instruction set architecture and implemented a simulator which embodies that instruction set.
		Software engineering principles were used to complete this project. Project was submitted as part of the
		IEEE Contest 2010 upon completion}
		{}{}
	\cventry{Spring 2009}{CMOS/VLSI Design, USF}{Team of 3}
		{\newline Designed an ASIC which would take input from a digital thermometer and output to a 7 segment display.
		The ASIC was to keep information such as maximum and minimum temperatures. Cadence Virtuoso was
		used to develop the circuit layout and hspice was used to ensure the circuit would function properly}
		{}{}
	\cventry{Spring 2009}{Networks, USF}{Team of 2}
		{\newline Designed client software which allowed clients to send messages to “friends.” Also designed server
		software to handle user registration and “friend” lists for clients. Both TCP and UDP protocols used}
		{}{}